### 2021-04-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

However, eliminating side-channel vulnerabilities from real-world software code base is not easy. First, some vulnerable implementations actually perform better. For example, RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Fixing vulnerabilities can introduce new weaknesses. We are in a dilemma between the performance and the security. Second, it is hard to detect side-channel leakages in reality. While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives. For example, recent tools like DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@. Further analysis shows 1,510 leaks can be dismissed. But that leaves 460 data-access leaks and 278 control-flow leaks. Many of these vulnerabilities have not been fixed by developers for a variety of reasons. Third, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being compromised~\cite{184415, aumuller2002fault} entirely, many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.

>>>>

However, eliminating side-channel vulnerabilities from real-world software code base is not easy. First, side-channels are a low-level problem in computer systems. As a non-functional property, it can be difficult for programmers to reason about or test.  While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives. Many of these vulnerabilities have not been fixed by developers for a variety of reasons. Second, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being compromised~\cite{184415, aumuller2002fault} entirely, many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.  Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance. It is a dilemma between the performance and the security.
